---
title: "README"
author: "John Schroeder"
date: "1/16/2020"
output: github_document
---

Introduction
=======
The following R project includes code necessary to run the simulation for the manuscript entitled "Mutualist and pathogen traits interact to affect plant community structure in a spatially explicit model." All functions necessary to run the simulation are included in Simulation_functions.R. We also include results from 50K simulations runs using random parameter values in Simulation_results_50K_random_runs.RData.

The following R packages are required to run the simulation
```{r,warning=FALSE, message=FALSE}
library(doSNOW) #For parallelizing simulation runs
library(randomForest) #For conducting random forest analyses between batches of runs (used for optimization)
library(abind) #For binding lists of results
library(poweRlaw) #For generating dispersal kernels
library(vegan)
```

Source code for the simulation functions:
```{r}
source("./Simulation_functions.R")
```

The following code chunks conduct an example simulation run using the parameter values presented in Table 1 of Schroeder et al. (2020, in review)
```{r}
numcores <- 4 #Define the number of cores to use to simultaneously run multiple simulations
cl <- parallel::makeCluster(numcores) #Create cluster
registerDoSNOW(cl) #Register cluster
```

Define parameter values and settings for simulation runs (this example runs simulations with identical parameter values four times):
```{r}
load("./RunFiles/position.RData")
number.of.runs <- 4
particle.positions <- as.data.frame(position[rep(1,number.of.runs),])
tree.species <- 5
trees.in.forest <- 499
mort <- 0.1
mortality.replacement.steps <- 3000
eliminate.feedback <- c(rep(FALSE,number.of.runs))
fix.feedback <- c(rep(FALSE,number.of.runs))
remove.mutualists <- c(rep(FALSE,number.of.runs))
remove.pathogens <- c(rep(FALSE,number.of.runs))
f.vals <- t(sapply(particle.positions[,4],function(x) {(c(1:tree.species-1)/(tree.species-1))*(1-x)+x}))
pb <- txtProgressBar(max = number.of.runs, style = 3)
progress <- function(n) setTxtProgressBar(pb, n)
opts <- list(progress = progress)
```

Run multiple simulations using the 'dopar' function, and store the output in a list called simulation.results:
```{r}
simulation.results <- foreach(g = particle.positions$g,
                                  h = particle.positions$h,
                                  b.t = particle.positions$b.t,
                                  s.m = particle.positions$s.m,
                                  b.m = particle.positions$b.m,
                                  alpha.m = particle.positions$alpha.m,
                                  gamma.m = particle.positions$gamma.m,
                                  r.m = particle.positions$r.m,
                                  q.m = particle.positions$q.m,
                                  c.m = particle.positions$c.m,
                                  s.p = particle.positions$s.p,
                                  b.p = particle.positions$b.p,
                                  alpha.p = particle.positions$alpha.p,
                                  gamma.p =particle.positions$gamma.p,
                                  r.p = particle.positions$r.p,
                                  q.p = particle.positions$q.p,
                                  c.p = particle.positions$c.p,
                                  fix.feedback = fix.feedback,
                                  eliminate.feedback = eliminate.feedback,
                                  remove.mutualists = remove.mutualists,
                                  remove.pathogens = remove.pathogens,
                                  index = c(1:number.of.runs),
                                  .packages = c("poweRlaw","vegan"), .options.snow = opts) %dopar%
        (
        psf.simulation(m = trees.in.forest,
                            mort = mort,
                            tree.species = tree.species,
                            mutualist.species.per.tree = 1,
                            pathogen.species.per.tree = 1,
                            time.steps = mortality.replacement.steps,
                            mutualist.effect.function.consp = mutualist.effect.function.consp, 
                            mutualist.effect.function.heterosp = mutualist.effect.function.heterosp,
                            pathogen.effect.function.consp = pathogen.effect.function.consp,
                            pathogen.effect.function.heterosp = pathogen.effect.function.heterosp,
                            g = g,
                            h = h,
                            s.p = s.p,
                            s.m = s.m,
                            b.p = b.p,
                            b.m = b.m,
                            b.t = b.t,
                            f.vals = rev(f.vals[index,]),
                            index = index,
                            gamma.m = gamma.m,
                            gamma.p = gamma.p,
                            r.m = r.m,
                            r.p = r.p,
                            q.m = q.m,
                            q.p = q.p,
                            c.m = c.m,
                            c.p = c.p,
                            alpha.m = alpha.m,
                            alpha.p = alpha.p,
                            fix.feedback = fix.feedback,
                            eliminate.feedback = eliminate.feedback,
                            remove.mutualists = remove.mutualists,
                            remove.pathogens = remove.pathogens,
                            initiate.forest.matrix = initiate.forest.matrix,
                            initiate.fungal.matrix = initiate.fungal.matrix,
                            trial.function = trial.function,
                            dispersal.function = dpldis,
                            microbe.dispersal.function = dpldis,
                            track.over.time = TRUE))
```




